### 2020-04-20 final_report/methodology.tex
add diagrams of neural net architectures
Finished draft of methodology - adaptive sampling section.

>>>>

All of the surrogate modelling techniques studied in this project face a shared challenge: their accuracy is limited by the quantity of training samples which are available from the expensive MC model. Adaptive sampling procedures can improve upon this limitation by taking advantage of statistical information which is accumulated during the training of any surrogate model. Rather than training the surrogate on a single sample set generated according to a fixed strategy, sample locations are chosen incrementally so as to best suit the model under consideration.

Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling. Garud's [1] "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain. We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space. MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution from the prior point. These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see [2] for a review).

Many researchers have embedded surrogate methods into MCMC strategies for parameter optimisation [3][4], in particular the ASMO-PODE algorithm [5] which makes use of MCMC-based adaptive sampling to attain greater surrogate precision around prospective optima. Our novel approach draws inspiration from ASMO-PODE, but instead uses MCMC to generate samples which increase surrogate precision throughout the entire parameter space.

\begin{wrapfigure}{r}{0.5\textwidth}
  \vspace{-35pt}
  \begin{center}
    \includegraphics[width=0.6\textwidth]{fig4_qassplan.png}
    \caption{Schematic of QASS algorithm}
    \label{fig:qassplan}
  \end{center}
  \vspace{-20pt}
\end{wrapfigure}

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS) to iteratively increment the training set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) [6] in parameter space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, test error values were calculated according to the representative error defined in [1]. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the primary training set, beginning another training epoch. An adaptive MCMC technique [7], which tunes an ellipsoidal proposal distribution to best fit the proposal distribution, was also implemented.

Literature review:

other MC-based surrogate approaches

Smart-Sampling Algorithm [1]

Single MCMC [2]

Reverse [3][4] ASMO-PODE [5]

CDM [6]

Adaptive MCMC [7]

[1] Garud, 2016
[2] Zhou, 2018
[3] Zhang, 2020
[4] Gong, 2017

[5] Ginting, 2011
[6] Solonen, 2012
[7] Zhang, 2012
